\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-05 k-planar.tex
more updates

@@

The purpose of this paper is to prove product structure theorems for several non-minor-closed classes of interest. Our results are the first of this type for non-minor-closed classes.

@@

\note{DW}{Use $\mathcal{S}$ for the given shortcut system and $\mathcal{P}$ for the partition?}

@@

@@

We first formally define $k$-planar graphs.  An \defin{embedded graph} $G$ is a graph with $V(G)\subset\R^2$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.} in $\R^2$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior.  A \defin{crossing} in an embedded graph $G$ is a triple $(p,vw,xy)$ with $p\in\R^2$, $vw,xy\in E(G)$ and such that $p\in (vw\cap xy)\setminus\{v,w,x,y\}$. An embedded graph $G$ is \defin{$k$-plane} if each edge of $G$ takes part in at most $k$ crossings. \note{DW}{We need at most two edges cross at a single point, so we can add a dummy vertex of degree 4, right?}  A (not necessarily embedded) graph $G'$ is \defin{$k$-planar} if there exists a $k$-plane graph $G$ isomorphic to $G'$. Under these definitions, $0$-planar graphs are exactly planar graphs and $0$-plane graphs are exactly plane graphs.

@@

\note{DW}{We can motivate \cref{1-planar} since treewidth 3 is best possible, and the planarity of $H$ is essential in the proof of \cref{1PlanarQueue}. Futher motivation comes from the open problem at the end of the paper. We need to argue this in the response and in the paper. The alternative is to remove \cref{sec-1-planar}? We could keep the statement of \cref{1-planar} in the paper and refer to the arXiv paper for the proof. What do you think? All this depends on whether we can fix the errors below. I vote to fix the errors, add more motivation for \cref{1-planar}, keep the theorem and the proof. }

@@

@@

\referee{2}{Page 15. Regarding the proof of Theorem 11, if it really is the same
	proof as the proof of Theorem 2, why not just prove Theorem 11 (from
	which Theorem 2 follows as a special case)?}

@@

>>>>

\note{DW}{Delete `from 1992' and  `from 2007'? replace ``going back to 1988~\citep{kannan.naor.ea:implicit-stoc,kannan.naor.ea:implicit}'' by 
	``starting with the work of \citet{kannan.naor.ea:implicit}''}

@@

The main purpose of this paper is to prove product structure theorems for several non-minor-closed classes of interest. Our results are the first of this type for non-minor-closed classes.

@@

\note{DW}{Use $\SS$ for the given shortcut system and $\PP$ for the partition?}

@@

\note{DW}{I think $\binom{k+t}{t}$ in \cref{general-bag-size} and $\binom{p+t}{t}$ in \cref{p-centered-treewidth} are no coincidence. The proofs are very similar. Worth exploring further?}

@@

We first formally define $k$-planar graphs.  An \defin{embedded graph} $G$ is a graph with $V(G)\subset\R^2$ in which each edge $vw\in E(G)$ is a curve\footnote{A \defin{curve} in a surface $\Sigma$ is a continuous function $f:[0,1]\to \Sigma$. The points $f(0)$ and $f(1)$ are called the \defin{endpoints} of the curve.  When there is no danger of misunderstanding we treat a curve $f$ as the point set $\{f(t):0\le t\le 1\}$.} in $\R^2$ with endpoints $v$ and $w$ and not containing any vertex of $G$ in its interior.  A \defin{crossing} in an embedded graph $G$ is a triple $(p,vw,xy)$ with $p\in\R^2$, $vw,xy\in E(G)$ and such that $p\in (vw\cap xy)\setminus\{v,w,x,y\}$. An embedded graph $G$ is \defin{$k$-plane} if each edge of $G$ takes part in at most $k$ crossings. \note{DW}{We need to assume that at most two edges cross at a single point, so we can add a dummy vertex of degree 4, right?}  A (not necessarily embedded) graph $G'$ is \defin{$k$-planar} if there exists a $k$-plane graph $G$ isomorphic to $G'$. Under these definitions, $0$-planar graphs are exactly planar graphs and $0$-plane graphs are exactly plane graphs.

@@

\note{DW}{We can motivate \cref{1-planar} since the graph drawing community particularly cares about 1-planar graphs, since treewidth 3 is best possible, and since the planarity of $H$ is essential in the proof of \cref{1PlanarQueue}. Futher motivation comes from the open problem at the end of the paper. We need to argue this in the response and in the paper. The alternative is to remove \cref{sec-1-planar}? We could keep the statement of \cref{1-planar} in the paper and refer to the arXiv paper for the proof. What do you think? All this depends on whether we can fix the errors below. I vote to fix the errors, add more motivation for \cref{1-planar}, keep the theorem and the proof. }

@@

\note{DW}{I agree we need more details. I am having trouble verifying this proof. }

@@

@@

\note{DW}{I don't want to do a complete restructuring. In our response, let's just say why we structure it the way we do.}
